Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
hscc17

By applying a state-of-the-art CEGIS engine we are now able to present a
tool that automatically \emph{generates} digital controllers for a given
plant model that are correct by construction.  This approach promises to
reduce the cost and time of development of digital control dramatically, and
requires considerably less expertise than methodologies driven by
verification.  Specifically, we synthesise controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{stable}.  Due to the complexity of such systems, we focus on linear
models with known configurations to perform parametric synthesis of the
controller dynamics.

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behaviour and the controller operates in both
discrete time and discrete state space.  The key insight of our approach is
that the problem can be translated into a \emph{single, joint domain}, which
represents a bi-simulation of the original, hybrid dynamics.  Given our
primary interest in stability despite digitisation effects, we have modelled
a digital equivalent of the plant by evaluating the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  The resulting closed-loop system is a program loop that
operates on bit-vectors encoded using fixed-point arithmetic with fixed word
length (FWL).  The deterministic effects of the FWL and
quantisation errors are incorporated into the model as an additive
uncertainty, which is taken into account during the CEGIS-based synthesis of
the control software for the plant.

@@

\item We designed and implemented an automatic approach for generating
  {\em corect-by-construction} digital controllers that is based on
  state-of-the-art inductive synthesis techniques.  Our application of
  program synthesis is non-trivial and requires addressing challenges
  specific to embedded control systems such as the effects of quantisers and
  FWL. In particular, we found that a two-stage verification engine
  that continuously refines the precision of the fixed-point
  representation is key to the performance of our approach yielding,
  in most cases, to a speed-up of at least two orders of magnitude over a
  conventional one-stage verification engine.

>>>>

By applying a state-of-the-art CEGIS engine we are now able to present a
tool that automatically \emph{generates} digital controllers for a given
continuous plant model that are correct by construction.  This approach promises to
reduce the cost and time of development of digital control dramatically, and
requires considerably less expertise than methodologies driven by
verification.  Specifically, we synthesise controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{stable}.  Due to the complexity of such systems, in this work we focus on linear
models with known configurations and perform parametric synthesis of stabilising digital controllers.

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behaviour whereas the controller operates in 
discrete time and over a quantised domain.  Our approach translates the problem into a single digital domain.  
Given our primary interest in stability despite digitisation effects, we have modelled
a digital equivalent of the plant by evaluating the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  The resulting closed-loop system is a program loop that
operates on bit-vectors encoded using fixed-point arithmetic with fixed word
length (FWL). The deterministic effects of the FWL and
quantisation errors are incorporated into the model as an additive
uncertainty, which is taken into account during the CEGIS-based synthesis of
the control software for the plant.

@@

\item We design and implement an automatic approach for generating
  {\em corect-by-construction} digital controllers that is based on
  state-of-the-art inductive synthesis techniques.  Our application of
  program synthesis is non-trivial and requires addressing challenges
  specific to embedded control systems, such as the effects of quantisers and
  FWL. In particular, we have found that a two-stage verification engine
  that continuously refines the precision of the fixed-point
  representation is key to the performance of our approach yielding,
  in most cases, to a speed-up of at least two orders of magnitude over a
  conventional one-stage verification engine.
